A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-20 BSS7782.tex
some minor update. Regretfully, did not have the time to really get to the paper. Better tomorrow

@@

We propose a formation mechanism for twin blue stragglers in compact
binaries that involves mass transfer from an evolved outer tertiary
companion on to the inner binary via a circumbinary disk.  We apply
our scenario to the observed double blue straggler system Binary 7782
in the old open cluster NGC 188, and show that its observed properties
are naturally reproduced within the context our proposed model.
Within the context of the hypothetical formation mechanism proposed
here, the presented work predicts the following properties for the
post-mass transfer double BS tertiary: (1) For the outer tertiary
orbit, the initial orbital period should lie between 220 days
$\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days \simon{Do you think that
  the initial binary could be as large as 1400 days?}, assuming
initial masses for the inner binary components of m$_{\rm 1} =$ 1.1
M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
mass of m$_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe overflow, the
outer star turns into a white dwarf (WD). There is a correlation
bewteen the mass of this WD and the outer orbital period in the sense
that a more massive white dwarfs will be on a wider orbit.  (3) The
rotational axes of the BSs in the inner binary should be aligned with
each other and the orbital plane of the outer tertiary WD. (4) The BSs
in the inner binary should have roughly equal masses, independent of
their initial masses.  This predicts that the initially lower mass MS
star should accrete the most, and should hence be enriched more
effectively by the accreted material.  This could be observable in the
surface layers of a radiative star (i.e., He, C and O enrichment if
the donor is an RGB star, and/or s-process elements if the donor is an
AGB star). (5) Twin BSs in compact binaries formed from the proposed
mechanism should be more frequent in younger clusters \simon{WHy not
  in the field?} with ages $\lesssim$ 4-6 Gyr, since the donor will
have a radiative envelope. (6) the orbital of the binary BS will be
tight (typically $\aplt 0.3$\,au) and close to circular ($e \aplt
0.2$).

@@

Blue straggler (BS) stars are brighter and bluer than the
main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
\citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.  Two
primary channels for BS formation have been proposed; mass transfer
from an evolved donor on to a main-sequence star in a binary star
system
\citep[e.g.][]{mccrea64,997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
and direct stellar collisions involving main-sequence stars possibly
mediated via binaries
\citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
Other possible, albeit related, formation mechanisms include mergers
of compact main-sequence binaries (ms, ms), and mergers of the inner
binaries \cite{+++} of hierarchical triple star systems induced by Lidov-Kozai
oscillations coupled with tidal damping \citep[e.g.][]{perets09}.

@@

We propose a formation channel for Binary 7782, and compact double BS
binaries in general, which involves mass transfer from an outer
tertiary companion on to an inner (ms, ms) binary.  In
section~\ref{dyn}, we constrain the range of initial (i.e., pre-mass
transfer) orbital parameters for a hypothetical outer tertiary
companion, using a combination of dynamical and stellar
evolution-based constraints.  In Section~\ref{sims} we present the
numerical simulations used to study the mass transfer process in our
hypothetical triple system, computed using the
\texttt{AMUSE}\cite{AMUSE} software package, in order to study the
evolution of the inner and outer orbital parameters during mass
transfer.  We summarize and discuss the implications of our results
for compact double BS binaries and, more generally, mass transfer in
stellar triples in Section~\ref{discussion}.

\section{Constraints on the present-day orbital parameters for a hypothesized tertiary companion in the compact BS Binary 7782} \label{dyn}

Consider a hierarchical triple system with component masses m$_{\rm
  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  For clarity we now assume both orbits, the inner as
well as the outer to have a small eccentricity and low inclination.
These assumptions are also supported by the population of observed
low-mass triples \cite{2010yCat..73890925T,moe18}.  This initial
configuration for our assumed formation scenario for Binary 7782,
described below, is depicted in Figure~\ref{fig:fig1}.

@@

We consider a scenario where the outer star is filling its Roche lobe
and transfers mass to the inner binary.  The mass transfer stream
gathers at the circularization radius a$_{\rm c}$, and forms a disk
around the inner binary.  Using conservation of angular momentum, we
equate the specific angular momentum of the accreted mass at the inner
Lagrangian point of the (outer) donor star to the final specific
angular momentum of the accretion stream at the circularization radius
about the inner binary, this results in
\begin{equation}
\label{eqn:specangmom1}
v_{\rm orb,3}(a_{\rm out} - R_{\rm L}) = v_{\rm orb,c}a_{\rm c},
\end{equation}
where R$_{\rm L}$ is the radius of the Roche lobe of the outer
tertiary companion, $a_{\rm c}$ is the semi-major axis of the orbit
about the inner binary corresponding to the circularization radius and
v$_{\rm orb,c}$ is the orbital velocity at $a_{\rm c}$.  The distance
from the center of mass corresponding to the outer tertiary companion
defined by the Roche lobe is given by Equation 2 in \citep{eggleton83}.
%\begin{equation}
%\label{eqn:roche}
%R_{\rm L} = \frac{0.49q^{2/3}}{0.6q^{2/3} + {\rm ln}(1 + q^{1/3})}a_{\rm out},
%\end{equation}
%where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$
%m$_{\rm 2}$).  
Combining Equation 2 in \citet{eggleton83} (with mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
Equation~\ref{eqn:specangmom1}, we can solve for the circularization
radius as a function of a$_{\rm out}$ and the assumed stellar masses:
\begin{equation}
\label{eqn:ac}
a_{\rm c} = a_{\rm out}(1 - R_{\rm L}).
\end{equation}
In order for a circumbinary disk to form around the inner binary, we
require that a$_{\rm in} <$ a$_{\rm c}$.

Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
  out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2}
= 0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3}
= 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the
circularization radius to the semi-major axis of the inner binary, for
which we require $a_{\rm c} > a_{\rm in}$, after folding in all
constraints from the requirements for dynamical stability (listed in
the caption of Figure~\ref{fig:fig2}), an outer tertiary that is Roche
lobe-filling, and a dynamically hard outer tertiary orbit.  Note that
the range of plotted orbital periods P$_{\rm in}$ corresponding to a
contact state for the inner binary lies outside the range of plotted
values for $P_{\rm in}$ (for components with radii of roughly 1
R$_{\odot}$), since it does not contribute significantly to
constraining the outer orbital properties of a hypothesized outer WD
tertiary.  The thick horizontal solid red line shows the allowed range
of outer semi-major axes, after folding in all of the aforementioned
criteria.  As is clear, this makes a relatively narrow prediction for
the allowed ranges of outer tertiary orbits, namely 2.2 $\times$
10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for
our assumed final donor mass.

@@

We perform simulations of a triple star system for which the outer star
overfills its Roche lobe while the inner binary remains detached. The
calculations start by evolving the three stars to the same age, which
is selected such that the outer-most star fills its Roche lobe.
Constraints for the initial conditions are derived in the previous
\S\, but in \S\,\ref{Sect:ICs} we summarize the adopted initial
conditions for the simulations.

Roche-lobe overflow in triples is modeled using a coupled integrator
to follow the complex hydrodynamics of the mass transfer from the
Roche-lobe filling outer star to the inner binary, while keeping track
of the gravitational dynamics of the stars.  The equations of motion
of the inner binary are solved using the symplectic direct N-body
integrator \texttt{Huayno} \citep{2012NewA...17..711P}. The
hydrodynamics is performed with the smoothed-particles hydrodynamics
code \texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
equation of state.  The two inner binary stars are treated as point
masses, but we allow them to accrete gas from the outer star.  This is
realized using sink-particles that co-move with the mass points in the
gravity code. While the inner two stars accrete mass, they also
accrete the corresponding amount of angular momentum from the gas.
The the N-body integrator accounts of this appropriately.  For the
radius of the sink particles we adopt $2 R_\odot$ for both stars.

@@

++++

@@

We adopt initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$
and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components,
and $m_{\rm 3} = 1.2$ M$_{\rm \odot}$ for the tertiary star.  We
evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
\cite{2011ApJS..192....3P} to a radius of about 1\,au.  By this time
the star has lost 0.13\,\MSun\, via a stellar wind.  We turned the
stellar evolution model, structure and temperature composition, into a
smoothed-particles representation using the module {\tt
  StellarModelInSPH} in AMUSE (see chapter 4 in \cite{AMUSE}).  We
replace the stellar core by a point mass to precent that all the
resolution will be in the central portion of the star instead of the
envelope. In a following step we relax the star using the
hydrodynamics solver. This relaxation process is realized in 100 steps
during which we reduce the velocity dispersion of individual SPH
particles to a glasseas structure \citep[see, for example, \S\,3.3 on
  page 40 in][]{1994astro.ph.10043W}.

With these parameters the orbital separation of the outer binary
becomes 3.86\,au, and the mass loss has driven a slight eccentricity
deviating from an initially circular orbit to about 0.0082 at the
moment of Roche-lobe overflow. We choose a relative initial
inclination of $i = 9^\circ$ between the inner and the outer orbits,
since observed stellar triples composed of low-mass stars have been
observed to favor co-planar configurations \citep{moe18}.
%NL: What are the initial orbital separations?  Why this choice of initial inclination? - I added a sentence and reference to justify it.

In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
system at the onset of Roche-lobe overflow.

@@

In fig.\,\ref{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_MvsTime_N80k_M012R100RSun1109MSun_a02au.pdf}
\caption{Evolution of the masses (normalized to those at the moment of
  RLOF) for each of the three stars in the simulated triple as a function of
  time for the first 1000\,days. (see fig.\,\ref{fig:topview_at_t0}
  for a face-on representation of the initial conditions and
  fig.\,\ref{fig:topview_at_t1000day} for the final conditions}.  The
green and orange dashed curves give the masses of the inner two stars,
whereas the solid blue curve is the mass of the outer most star.
\label{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
\end{figure}

The orbital evolution of the inner binary circumreferenced by a disk
tends to evove by the accretion of mass and angular momentum. As a
consequence, the two stars in the binary accumulate mass, and their
orbit shrinks. The orbital evolution can be approximated, to first order, by:
\begin{equation}
  d\ln a \over dt   = - d\ln m_{\rm in} \over dt,
\end{equation}
where $a$ and $m_{\rm in}$ are the semimajor-axis and total mass in
the inner binary.  In the simulations we measure ${\dln a \over dt}
\simeq -0.0843$\,Myr$^{-1}$.

@@

\item For the predicted outer tertiary orbit, the present-day semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.

>>>>

\def\apgt{\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
\def\aplt{\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }

@@

We propose a formation mechanism for twin blue stragglers in compact
binaries that involves mass transfer from an evolved outer tertiary
companion on to the inner binary via a circumbinary disk.  We apply
our scenario to the observed double blue straggler system Binary 7782
in the old open cluster NGC 188, and show that its observed properties
are naturally reproduced within the context our proposed model.
Within the context of the hypothetical formation mechanism proposed
here, the presented work predicts the following properties for the
post-mass transfer double BS tertiary: (1) For the outer tertiary
orbit, the initial orbital period should lie between 220 days
$\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days \simon{Do you think that
  the initial binary could be as large as 1400 days?}, assuming
initial masses for the inner binary components of $m_{\rm 1} = 1.1$
M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe overflow, the
outer star turns into a white dwarf (WD). There is a correlation
bewteen the mass of this WD and the outer orbital period in the sense
that a more massive white dwarfs will be on a wider orbit.  (3) The
rotational axes of the BSs in the inner binary should be aligned with
each other and the orbital plane of the outer tertiary WD. (4) The BSs
in the inner binary should have roughly equal masses, independent of
their initial masses.  This predicts that the initially lower mass MS
star should accrete the most, and should hence be enriched more
effectively by the accreted material.  This could be observable in the
surface layers of a radiative star (i.e., He, C and O enrichment if
the donor is an RGB star, and/or s-process elements if the donor is an
AGB star). (5) Twin BSs in compact binaries formed from the proposed
mechanism should be more frequent in younger clusters \simon{WHy not
  in the field?} with ages $\lesssim$ 4-6 Gyr, since the donor will
have a radiative envelope. (6) the orbital of the binary BS will be
tight (typically $\aplt 0.3$\,au) and close to circular ($e \aplt
0.2$).

@@

Blue straggler (BS) stars are brighter and bluer than the
main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
\citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.  Two
primary channels for BS formation have been proposed; mass transfer
from an evolved donor on to a main-sequence star in a binary star
system
\citep[e.g.][]{mccrea64,1997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
and direct stellar collisions involving main-sequence stars possibly
mediated via binaries
\citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
Other possible, albeit related, formation mechanisms include mergers
of close main-sequence binaries (ms, ms) \cite{2018arXiv181100058P},
and mergers of the inner binaries of hierarchical triple star systems
induced by Lidov-Kozai oscillations coupled with tidal damping
\citep[e.g.][]{perets09}.

@@

We propose a formation channel for Binary 7782, and compact double BS
binaries in general, which involves mass transfer from an outer
tertiary companion on to an inner (ms, ms) binary.  In
section~\ref{sect:dyn}, we constrain the range of initial (i.e., pre-mass
transfer) orbital parameters for a hypothetical outer tertiary
companion, using a combination of dynamical and stellar
evolution-based constraints.  In Section~\ref{sims} we present the
numerical simulations used to study the mass transfer process in our
hypothetical triple system, computed using the
\texttt{AMUSE}\cite{AMUSE} software package, in order to study the
evolution of the inner and outer orbital parameters during mass
transfer.  We summarize and discuss the implications of our results
for compact double BS binaries and, more generally, mass transfer in
stellar triples in Section~\ref{discussion}.

\section{Constraints on the present-day orbital parameters for a hypothesized
         tertiary companion in the compact BS Binary 7782} \label{sect:dyn}

Consider a hierarchical triple system with component masses $m_{\rm
  1}$ and $m_{\rm 2}$ for the inner binary, and mass $m_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  For clarity we now assume both orbits, the inner as
well as the outer to have a small eccentricity and low inclination.
These assumptions are also supported by the population of observed
low-mass triples \cite{2010yCat..73890925T,moe18}.  This initial
configuration for our assumed formation scenario for Binary 7782,
described below, is depicted in Figure~\ref{fig:fig1}.

@@

We consider a scenario where the outer star is filling its Roche lobe
and transfers mass to the inner binary.  The mass transfer stream
gathers at the circularization radius a$_{\rm c}$, and forms a disk
around the inner binary.  Using conservation of angular momentum, we
equate the specific angular momentum of the accreted mass at the inner
Lagrangian point of the (outer) donor star to the final specific
angular momentum of the accretion stream at the circularization radius
about the inner binary, this results in
\begin{equation}
\label{eqn:specangmom1}
v_{\rm orb,3}(a_{\rm out} - R_{\rm L}) = v_{\rm orb,c}a_{\rm c},
\end{equation}
where R$_{\rm L}$ is the radius of the Roche lobe of the outer
tertiary companion, $a_{\rm c}$ is the semi-major axis of the orbit
about the inner binary corresponding to the circularization radius and
v$_{\rm orb,c}$ is the orbital velocity at $a_{\rm c}$.  The distance
from the center of mass corresponding to the outer tertiary companion
defined by the Roche lobe is given by Equation 2 in
\citep{eggleton83}.  Combining Equation 2 in \citet{eggleton83} (with
mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
Equation~\ref{eqn:specangmom1}, we can solve for the circularization
radius as a function of a$_{\rm out}$ and the assumed stellar masses:
\begin{equation}
\label{eqn:ac}
a_{\rm c} = a_{\rm out}(1 - R_{\rm L}).
\end{equation}
In order for a circumbinary disk to form around the inner binary, we
require that a$_{\rm in} <$ a$_{\rm c}$.

Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
  out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2}
= 0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3}
= 1.4 $M$_{\rm \odot}$ for the outer tertiary.  We compare the
circularization radius to the semi-major axis of the inner binary, for
which we require $a_{\rm c} > a_{\rm in}$, after folding in all
constraints from the requirements for dynamical stability (listed in
the caption of Figure~\ref{fig:fig2}), an outer tertiary that is Roche
lobe-filling, and a dynamically hard outer tertiary orbit.  Note that
the range of plotted orbital periods P$_{\rm in}$ corresponding to a
contact state for the inner binary lies outside the range of plotted
values for $P_{\rm in}$ (for components with radii of roughly 1
R$_{\odot}$), since it does not contribute significantly to
constraining the outer orbital properties of a hypothesized outer WD
tertiary.  The thick horizontal solid red line shows the allowed range
of outer semi-major axes, after folding in all of the aforementioned
criteria.  As is clear, this makes a relatively narrow prediction for
the allowed ranges of outer tertiary orbits, namely 2.2 $\times$
10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for
our assumed final donor mass.

@@

We perform simulations of a triple star system for which the outer
star overfills its Roche lobe while the inner binary remains
detached. The calculations start by evolving the three stars to the
same age, which is selected such that the outer-most star fills its
Roche lobe.  First order constraints for the initial conditions are
derived in the previous \S\, but in \S\,\ref{Sect:ICs} we summarize
the adopted initial conditions for the more detailed simulations.

Roche-lobe overflow in triples is modeled using a coupled integrator
to follow the complex hydrodynamics of the mass transfer from the
Roche-lobe filling outer star to the inner binary, while keeping track
of the gravitational dynamics of the stars.  The equations of motion
of the inner binary are solved using the symplectic direct N-body
integrator \texttt{Huayno} \citep{2012NewA...17..711P}. The
hydrodynamics is performed with the smoothed-particles hydrodynamics
code \texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
equation of state.  The two inner binary stars are treated as point
masses, but we allow them to accrete mass and angular momentum from
the gas liberated by the outer star.  This is realized using
sink-particles that co-move with the mass points in the gravity
code. While the inner two stars accrete mass, they also accrete the
corresponding amount of angular momentum from the gas.  The the N-body
integrator accounts of this appropriately.  For the radius of the sink
particles we adopt $2 R_\odot$ for both stars.

@@

@@

We adopt initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$
and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components,
and between $m_{\rm 3} = 1.2$ and $m_{\rm 3} = 1.4$ M$_{\rm \odot}$
for the tertiary star.  We evolve the tertiary star using the MESA
stellar-evolution code \cite{2011ApJS..192....3P} to a radius of about
1\,au.  By this time the star has lost 0.13\,\MSun\, via a stellar
wind.  We subsequently turn the stellar-evolution model, structure,
temperature and composition, into a smoothed-particles representation
using the module {\tt StellarModelInSPH} in AMUSE (see chapter 4 in
\cite{AMUSE}).  We replace the stellar core by a point mass to prevent
that all the resolution will be in the central portion of the star
instead of the envelope. In a following step we relax the star using
the hydrodynamics solver. This relaxation process is realized in 100
steps during which we reduce the velocity dispersion of individual SPH
particles to a glasseas structure \citep[see, for example, \S\,3.3 on
  page 40 in][]{1994astro.ph.10043W}. During this procedure the
gaseous envelope of the star tends to expand by about 20\%.  To
detemrine the radius of the eventual star we calculate Lagrangian
radii and use the distance to the stellar center which contains 90\%
of it's mass. This 90\% mass-radius we consider as the stellar radius,
and match it with the Roche-lobe of the outer orbit.

With these parameters the orbital separation of the outer binary
becomes $\sim 3.86$\,au, and we adopt the outer orbit to be circular.
We choose a relative initial inclination between the inner and the
outer orbit of $i = 0^\circ$, $i = 9^\circ$ and $i = 180^\circ$.  The
first two choices are motivated by observed stellar triples composed
of low-mass stars which have been observed to favor co-planar
configurations \citep{moe18}. To test the effect of a retrogade
orbiting triple we include the $i = 180^\circ$ case.
% NL: What are the initial orbital separations?  Why this choice of
% initial inclination? - I added a sentence and reference to justify
% it.
In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
system at the onset of Roche-lobe overflow.

@@

In fig.\,\ref{fig:mass_vs_semimajor_axis}

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_mass_vs_semimajor_axis.pdf}
  \caption{Evolution of the total mass of the inner binary as a
    function of the orbital separation for four calculations with
    somewhat different initial conditions (see legend).  The initial
    binary for the orange curve is presented in
    fig.\,\ref{fig:topview_at_t0}, and in
    fig.\,\ref{fig:topview_at_t1000day} we present the final
    conditions.
\label{fig:mass_vs_semimajor_axis}}
\end{figure}

The orbital evolution of the inner binary circumreferenced by a disk
tends to evove by the accretion of mass and angular momentum. As a
consequence, the two stars in the binary accumulate mass, and their
orbit shrinks. The orbital evolution can be approximated, to first order, by:
\begin{equation}
  {d\ln a \over dt}   = {-d\ln m_{\rm in} \over dt},
\end{equation}
where $a$ and $m_{\rm in}$ are the semimajor-axis and total mass in
the inner binary.  In the simulations we measure ${d\ln a \over dt}
\simeq -0.0843$\,Myr$^{-1}$.

@@

\item For the predicted outer tertiary orbit, the present-day semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$ M$_{\odot}$ and an outer tertiary mass of $m_{\rm 3} = 1.4 $M$_{\odot}$.
